---
title: "Descriptive statistics"
author: "IBRAHIM KASSOUM Habibou"
date: "`r Sys.Date()`"
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, error=FALSE)
```



```{r}
rm(list=ls())
```

## Importing library

```{r Package needed, results = "hide"}


## Importing library
### List of required packages
required_packages <- c("tidyverse","janitor" ,"readr","dplyr", "flextable","gtsummary","ggthemes")

# Check if packages are installed
missing_packages <- setdiff(required_packages, installed.packages()[,"Package"])

### Install missing packages
if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

### Load all packages
lapply(required_packages, library, character.only = TRUE)


# if not already installed
#install.packages('devtools', repos = 'http://cran.us.r-project.org') 

# note: "V" is capitalized
devtools::install_github('xuyiqing/panelView') 

```


```{r}
# Read excel files data for the r1, r2 and r3

## For r1
df_r1_hh <- readxl::read_excel("output/data/r1_hh.xlsx")
df_r1_anthr1 <- readxl::read_excel("output/data/r1_overfive.xlsx")
df_r1_anthr2 <- readxl::read_excel("output/data/r1_underfive.xlsx")

## For r2
df_r2_hh <- readxl::read_excel("output/data/r2_hh.xlsx")
df_r2_anthr1 <- readxl::read_excel("output/data/r2_overfive.xlsx")
df_r2_anthr2 <- readxl::read_excel("output/data/r2_underfive.xlsx")

## For r3
df_r3_hh <- readxl::read_excel("output/data/r3_hh.xlsx")
df_r3_anthr1 <- readxl::read_excel("output/data/r3_overfive.xlsx")
df_r3_anthr2 <- readxl::read_excel("output/data/r3_underfive.xlsx")

```

```{r}


## Final dataset
df_global_corrected <- readxl::read_excel("output/data/df_global_corrected.xlsx", 
    col_types = c("skip", "text", "text", 
        "numeric", "numeric", "text", "text", 
        "text", "text", "numeric", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "numeric", 
        "numeric", "numeric", "numeric"))

df_global <- readxl::read_excel("output/data/df_global.xlsx", 
    col_types = c("skip", "text", "text", 
        "numeric", "numeric", "text", "text", 
        "text", "text", "numeric", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "numeric", 
        "numeric", "numeric","numeric"))
```

```{r}
## define custom test
fisher.test.simulate.p.values <- function(data, variable, by, ...) {
  result <- list()
  test_results <- stats::fisher.test(data[[variable]], data[[by]], simulate.p.value = TRUE)
  result$p <- test_results$p.value
  result$test <- test_results$method
  result
}
```


## Analysis of missing values and migration or attrition by region and migration.


### Splitted hh

```{r}
df_r1_hh %>% 

  # Selecting relevant variables
   select(hh_split_r2,hh_split_r3,interview_status_r2,interview_status_r3,affected_upazila) %>% 
  
mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       interview_status_r2 ~ "Interview status in R2",
       interview_status_r3 ~ "Interview status R3",
       hh_split_r2  ~ "Hh. split from R1 to R2",
       hh_split_r3 ~ "Hh. split from R1 to R3"),
    
    type = list(hh_split_r2 ~ "dichotomous", hh_split_r3 ~ "dichotomous"),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```


```{r}
# remove the splitted hh
df_r1_hh %>% 

  filter(hh_split_r2==0 & hh_split_r3==0) %>% 
  # Selecting relevant variables
   select(hh_split_r2,hh_split_r3,interview_status_r2,interview_status_r3,affected_upazila) %>% 
  
mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = affected_upazila, 
     label = list(
       interview_status_r2 ~ "Interview status in R2",
       interview_status_r3 ~ "Interview status R3",
       hh_split_r2  ~ "Hh. split from R1 to R2",
       hh_split_r3 ~ "Hh. split from R1 to R3"),
    
    type = list(hh_split_r2 ~ "dichotomous", hh_split_r3 ~ "dichotomous"),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "") %>% 
  add_overall(last=TRUE)
```


```{r}

df_r2_hh %>% 
  distinct(hh_id_parent, .keep_all = TRUE) %>% 
  # Selecting relevant variables
  # , labels = c("No affected district", "Affected district"),
   select(hh_split, affected_upazila) %>% 
  mutate(sample='round 2',      
         hh_split = factor(hh_split, levels = c("0", "1"),labels = c("No", "Yes"),ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>% 
  
  plyr::rbind.fill(
    #For the sibling dataset
    df_r3_hh %>%
      distinct(hh_id_parent, .keep_all = TRUE) %>% 
  # Selecting relevant variables
   select(hh_split, affected_upazila) %>% 
  #rename(affected_upazila=Affected_district) %>% 
   mutate( 
     sample='round 3',
     hh_split = factor(hh_split, levels = c("0", "1"), labels = c("No", "Yes"), ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
    tbl_strata(
    strata = sample,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
      tbl_summary(
    by = affected_upazila, 
      label = list(
        hh_split ~ "Household split (1=Yes, 0=No)"
    #    height_cm ~ "height (cm)",
    #    hhm_sex ~ "Sex",
    #    hhm_age ~ "age (in year)",
    #    relation_hhh ~ "relation with the head",
    #    if_not_measured_why ~ "Why missing"
    #    
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    # Add difference statistics to the table
    #add_difference(),
    .header = "**{strata}**, N = {n}") #%>%
  #as_gt() %>%
  #gt::gtsave('desc_table_summary.tex', path = here::here())
```


```{r}

# df_r2_hh %>% 
#   #distinct(hh_id_parent, .keep_all = TRUE) %>% 
#   # Selecting relevant variables
#   # , labels = c("No affected district", "Affected district"),
#    select(hh_split_bis, affected_upazila) %>% 
#   mutate(sample='round 2',      
#          hh_split_bis = factor(hh_split_bis, levels = c("0", "1"),labels = c("No", "Yes"),ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>% 
#   
#   plyr::rbind.fill(
#     #For the sibling dataset
#     df_r3_hh %>%
#       #distinct(hh_id_parent, .keep_all = TRUE) %>% 
#   # Selecting relevant variables
#    select(hh_split_bis, affected_upazila) %>% 
#   #rename(affected_upazila=Affected_district) %>% 
#    mutate( 
#      sample='round 3',
#      hh_split_bis = factor(hh_split_bis, levels = c("0", "1"), labels = c("No", "Yes"), ordered = TRUE), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
#     tbl_strata(
#     strata = sample,
#     .tbl_fun =
#       ~ .x %>%
#       # Generate a summary table using "tbl_summary" for the specified columns
#       tbl_summary(
#     by = affected_upazila, 
#       label = list(
#         hh_split_bis ~ "Household split infant (1=Yes, 0=No)"
#     #    height_cm ~ "height (cm)",
#     #    hhm_sex ~ "Sex",
#     #    hhm_age ~ "age (in year)",
#     #    relation_hhh ~ "relation with the head",
#     #    if_not_measured_why ~ "Why missing"
#     #    
#      ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(0,2),
#     missing = "always"
#   ) %>%
#       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
#       # Modify the table header to provide a descriptive label
#       modify_header(label ~ ""),
#     # Add difference statistics to the table
#     #add_difference(),
#     .header = "**{strata}**, N = {n}") #%>%
#   #as_gt() %>%
#   #gt::gtsave('desc_table_summary.tex', path = here::here())
```



### Interview status

Theses tables summarize the interview status for hh survey in round 2 (before the TC Mora) and in round 3 (after the TC Mora).

4690 hhs in round 3 have completed informations, I will take these to see how it affected. I should have at most 4690 household in R1 and R2 
```{r}


df_r1_hh %>% 

  # if you don't remove those who split between R1 and R2 you don't take into account the hh that split and disapear during R3.
  filter(hh_split_r2==0 & hh_split_r3==0) %>% 
  # Selecting relevant variables
   select(interview_status_r2,interview_status_r3) %>% 
  

      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r3, 
     label = list(
       interview_status_r2 ~ "Status R2",
       interview_status_r3 ~ "Status R3"),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "**Status R3**") 
```



```{r}
df_r1_hh %>% 

  # Selecting relevant variables
   select(interview_status_r2,interview_status_r3,affected_upazila) %>% 
     mutate(
       affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>% 
    tbl_strata(
    strata = affected_upazila,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r3, 
     label = list(
       interview_status_r2 ~ "Status R2",
       interview_status_r3 ~ "Status R3"),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    # Add difference statistics to the table
    #add_difference(),
    .header = "**{strata}**, N = {n}") #%>%
```


Here is 4603 (98.14 percent) hh for which information on the R2 is available. The remaining 87 didn't complete the information on R2 but complete the information on R1. The 65 remaining hh migrated in r2 but complete the survey in r3 (very strange). They were able to identify in r3 were the hh migrated too (where it go). I keep them in the data.

R3 = 4690
R2 = 4603-(87) = 4603
R1 = 4690
```{r}

df_r1_hh %>% 

  # if you don't remove those who split between R1 and R2 you don't take into account the hh that split and disapear during R3.
  filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 

mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
  # Selecting relevant variables
   select(interview_status_r2,affected_upazila, hh_size) %>% 
  

      # Generate a summary table using "tbl_summary" for the specified columns
    tbl_summary(
    by = interview_status_r2, 
     label = list(
       affected_upazila ~ "Affected_upazila",
       hh_size ~ "hh size"
       ),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    
    missing_text = "(Missing)",
    digits = list(hh_size ~ c(2, 2)),
    missing = "ifany"
  ) %>%
       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>% 
  modify_header(label ~ "**Status R3**") 

```




### Hh's head religion

```{r}

df_r1_hh %>% 
   select(hh_head_religion, affected_upazila) %>% 
  mutate(sample='round 1',      
         hh_head_religion = factor(hh_head_religion), 
         affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
  
  plyr::rbind.fill(df_r2_hh %>% 
   select(hh_head_religion, affected_upazila) %>% 
  mutate(sample='round 2',      
         hh_head_religion = factor(hh_head_religion), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>% 
  
  plyr::rbind.fill(
    df_r3_hh %>%
  # Selecting relevant variables
   select(hh_head_religion, affected_upazila) %>% 
   mutate( 
     sample='round 3',
     hh_head_religion = factor(hh_head_religion), 
     affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
    tbl_strata(
    strata = sample,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
      tbl_summary(
    by = affected_upazila, 
      label = list(
        hh_head_religion ~ "hh head religion"
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    .header = "**{strata}**, N = {n}") 
```

```{r}
df_r1_hh %>% 
  #distinct(hh_id_parent, .keep_all = TRUE) %>% 
  # Selecting relevant variables
  # , labels = c("No affected district", "Affected district"),
   select(hh_head_religion, interview_status_r2, interview_status_r3) %>% 
  mutate(
         #interview_status = factor(interview_status),
         interview_status_r2 = factor(interview_status_r2), 
         interview_status_r3 = factor(interview_status_r3)) %>% 
  
      # Generate a summary table using "tbl_summary" for the specified columns
  tbl_summary(
  by = hh_head_religion, 
      label = list(
        hh_head_religion ~ "hh head religion",
        #interview_status ~ "interview status round 1",
        interview_status_r2 ~ "interview status round 2",
        interview_status_r3 ~ "interview status round 3"
    #    hhm_age ~ "age (in year)",
    #    relation_hhh ~ "relation with the head",
    #    if_not_measured_why ~ "Why missing"
    #    
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) 
  #as_gt() %>%
  #gt::gtsave('desc_table_summary.tex', path = here::here())
```


### Hh head ethnicity

```{r}

df_r1_hh %>% 
   select(hh_ethnic_group, affected_upazila) %>% 
  mutate(sample='round 1',      
         hh_ethnic_group = factor(hh_ethnic_group), 
         affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE)) %>%
  
  plyr::rbind.fill(df_r2_hh %>% 
   select(hh_ethnic_group, affected_upazila) %>% 
  mutate(sample='round 2',      
         hh_ethnic_group = factor(hh_ethnic_group), affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>% 
  
  plyr::rbind.fill(
    df_r3_hh %>%
  # Selecting relevant variables
   select(hh_ethnic_group, affected_upazila) %>% 
   mutate( 
     sample='round 3',
     hh_ethnic_group = factor(hh_ethnic_group), 
     affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected", "Affected"), ordered = TRUE))) %>%
    tbl_strata(
    strata = sample,
    .tbl_fun =
      ~ .x %>%
      # Generate a summary table using "tbl_summary" for the specified columns
      tbl_summary(
    by = affected_upazila, 
      label = list(
        hh_ethnic_group ~ "hh head ethnic group"
     ),
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)",
    digits = everything() ~ c(0,2),
    missing = "always"
  ) %>%
      add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
      # Modify the table header to provide a descriptive label
      modify_header(label ~ ""),
    .header = "**{strata}**, N = {n}") 
```

```{r}
# 
# df_r1_hh %>% 
# 
#   # Selecting relevant variables
#    select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh,affected_upazila) %>% 
#   mutate(sample='round 1') %>% 
#   
#   plyr::rbind.fill(
#     #For the sibling dataset
#     r2_data %>%
# select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh, affected_upazila) %>% 
#   #rename(affected_upazila=Affected_district) %>% 
#    mutate( 
#      sample='round 2',
#      affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected district", "Affected district"), ordered = TRUE)) %>% 
#   filter(!is.na(if_not_measured_why))) %>%
# 
#   tbl_strata(
#     strata = sample,
#     .tbl_fun =
#       ~ .x %>%
#       # Generate a summary table using "tbl_summary" for the specified columns
#       tbl_summary(
#     by = affected_upazila, 
#      label = list(
#        weight_kg ~ "weight (kg)",
#        height_cm ~ "height (cm)",
#        hhm_sex ~ "Sex",
#        hhm_age ~ "age (in year)",
#        relation_hhh ~ "relation with the head",
#        if_not_measured_why ~ "Why missing"
#        
#     ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(2,2),
#     missing = "always"
#   ) %>%
#       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
#       # Modify the table header to provide a descriptive label
#       modify_header(label ~ "Characteristics of children"),
#     # Add difference statistics to the table
#     #add_difference(),
#     .header = "**{strata}**, N = {n}") #%>%
#   #as_gt() %>%
#   #gt::gtsave('desc_table_summary.tex', path = here::here())
```

```{r}

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0) %>% 
      select(hh_id) %>% 
      pull()

all_comb <- df_r1_hh %>%
            select(hh_id,survey_round) %>% 
            filter(hh_id %in% lst_menage) %>% 
            plyr::rbind.fill(df_r2_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            plyr::rbind.fill(df_r3_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            expand(hh_id,survey_round)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_r1_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year) %>% 
          filter(hh_id %in% lst_menage)%>% 
          plyr::rbind.fill(df_r2_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
          plyr::rbind.fill(df_r3_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
  dplyr::right_join(all_comb) %>% 
  mutate(
         affected_upazila = ifelse(is.na(hh_size), NA, affected_upazila),
         treat_group = ifelse(is.na(hh_size), NA, treat_group))
# survey_year = ifelse(survey_round==1,2011,
#                               ifelse(survey_round==2,2015,
#                                      ifelse(survey_round==3,2018,NA))),

panelView::panelview( 1 ~ treat_group, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("hh_id","survey_year"), display.all = TRUE,
          xlab = "Nbr household", ylab = "", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, collapse.history = "TRUE", main = "Traitement status")
```


```{r}
# df_global %>% 
#   mutate(survey_round=as.numeric(survey_round)) %>% 
#   filter(hh_split==0)
#   group_by(member_id) %>% 
#   summarise(n=n(), matot= sum(survey_round)) 

# used expand to create 
# Na because unborn vs NA
# niveau ménage

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 
      select(hh_id) %>% 
      pull()

all_comb <- df_r1_hh %>%
            select(hh_id,survey_round) %>% 
            filter(hh_id %in% lst_menage) %>% 
            plyr::rbind.fill(df_r2_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            plyr::rbind.fill(df_r3_hh %>%
            select(hh_id,survey_round)%>% 
            filter(hh_id %in% lst_menage)) %>% 
            expand(hh_id,survey_round)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_r1_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year) %>% 
          filter(hh_id %in% lst_menage)%>% 
          plyr::rbind.fill(df_r2_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
          plyr::rbind.fill(df_r3_hh %>%
          select(hh_id,survey_round, hh_size, affected_upazila,treat_group, survey_year)%>% 
          filter(hh_id %in% lst_menage))%>% 
  dplyr::right_join(all_comb) %>% 
  mutate(
         affected_upazila = ifelse(is.na(hh_size), NA, affected_upazila),
         treat_group = ifelse(is.na(hh_size), NA, treat_group))
# survey_year = ifelse(survey_round==1,2011,
#                               ifelse(survey_round==2,2015,
#                                      ifelse(survey_round==3,2018,NA))),

panelView::panelview( 1 ~ treat_group, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("hh_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr household", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, shade.post = TRUE, collapse.history = "TRUE", main = "Traitement status")
```

## Study Variables

### Socio-demographic variables

### Filtering to obtained only needed

```{r}
# niveau individus

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 
      select(hh_id) %>% 
      pull()

all_comb <- df_global %>%
            select(hh_id,hhm_id, member_id, survey_year) %>% 
            filter(hh_id %in% lst_menage) %>% 
            expand(member_id,survey_year)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_global %>%
            select(hh_id,hhm_id, member_id, survey_year, affected_upazila, treat_group, height_cm, weight_kg) %>% 
            filter(hh_id %in% lst_menage) %>% 
  dplyr::right_join(all_comb) #%>% 
  # mutate(
  #        affected_upazila = ifelse(is.na(hh_size), NA, affected_upazila),
  #        treat_group = ifelse(is.na(hh_size), NA, treat_group))
# survey_year = ifelse(survey_round==1,2011,
#                               ifelse(survey_round==2,2015,
#                                      ifelse(survey_round==3,2018,NA))),

panelView::panelview(weight_kg ~ treat_group + height_cm, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("member_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr individuals", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, shade.post = TRUE, collapse.history = "TRUE", main = "Traitement status")
```

```{r}
# niveau individus

lst_menage = df_r1_hh %>% 
      filter(hh_split_r2==0 & hh_split_r3==0 & interview_status_r3=="Complete") %>% 
      select(hh_id) %>% 
      pull()

lst_ind <- df_r3_anthr2 %>% 
            select(hh_id,member_id, hhm_status, hhm_age) %>%
            filter(hh_id %in% lst_menage & hhm_status=="Both previous round and current round member" & hhm_age >= 3) %>% 
            plyr::rbind.fill(df_r3_anthr1 %>% 
            select(hh_id,member_id, hhm_status, hhm_age) %>% 
            filter(hh_id %in% lst_menage & hhm_status=="Both previous round and current round member" & hhm_age < 20)) %>% 
            # filter(hh_id %in% lst_menage) %>% 
            # filter(hhm_status=="Both previous round and current round member") %>% 
            # filter(hhm_age >= 3 & hhm_age < 20) %>% 
            select(member_id) %>% 
            pull()

all_comb <- df_global %>%
            dplyr::select(member_id, survey_year) %>% 
            dplyr::filter(member_id %in% lst_ind) %>% 
            expand(member_id,survey_year)

# Use with `right_join()` to fill in missing rows (in data)
all_comb <- df_global %>%
            select(hh_id,hhm_id, member_id, survey_year, affected_upazila, treat_group, height_cm, weight_kg) %>% 
            filter(hh_id %in% lst_menage) %>% 
  dplyr::right_join(all_comb) 

panelView::panelview(weight_kg ~ treat_group + height_cm, gridOff = TRUE, by.timing = TRUE,
          data = all_comb, index = c("member_id","survey_year"), display.all = TRUE,
          xlab = "Year", ylab = "Nbr individuals", pre.post = TRUE, by.unit=TRUE,  background = "white",cex.main = 20, cex.axis= 8, cex.lab = 12, cex.legend = 12, shade.post = TRUE, collapse.history = "TRUE", main = "Traitement status")
```


#### Kid Sex/gender

```{r, results='hold', include = TRUE, warning=FALSE, echo = FALSE}

#
# r1_data %>%
#
#   # Selecting relevant variables
#   select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh, affected_upazila) %>%
#   #rename(affected_upazila=Affected_district) %>%
#    mutate(affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected district", "Affected district"), ordered = TRUE)) %>%
#   # Generate a summary table using "tbl_summary" for the specified columns
#   tbl_summary(
#     by = affected_upazila,
#      label = list(
#        weight_kg ~ "weight (kg)",
#        height_cm ~ "height (cm)",
#        hhm_sex ~ "Sex",
#        hhm_age ~ "age (in year)",
#        relation_hhh ~ "relation with the head",
#        if_not_measured_why ~ "Why missing"
#
#     ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(2,2),
#     missing = "always"
#   ) %>%
#     modify_caption("**R1**") %>%
#   # Modify the table header to provide a descriptive label
#   modify_header(label ~ "Affected Upazila") %>%
#   add_overall() %>%
#   add_n()%>%
#   # Add difference statistics to the table
#   add_difference()

#
#
# r1_data %>%
#
#   # Selecting relevant variables
#    select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh,affected_upazila) %>%
#   mutate(sample='round 1') %>%
#
#   plyr::rbind.fill(
#     #For the sibling dataset
#     r2_data %>%
# select(weight_kg,height_cm,if_not_measured_why,hhm_sex,hhm_age,relation_hhh, affected_upazila) %>%
#   #rename(affected_upazila=Affected_district) %>%
#    mutate(
#      sample='round 2',
#      affected_upazila = factor(affected_upazila, levels = c("0", "1"), labels = c("No affected district", "Affected district"), ordered = TRUE)) %>%
#   filter(!is.na(if_not_measured_why))) %>%
#
#   tbl_strata(
#     strata = sample,
#     .tbl_fun =
#       ~ .x %>%
#       # Generate a summary table using "tbl_summary" for the specified columns
#       tbl_summary(
#     by = affected_upazila,
#      label = list(
#        weight_kg ~ "weight (kg)",
#        height_cm ~ "height (cm)",
#        hhm_sex ~ "Sex",
#        hhm_age ~ "age (in year)",
#        relation_hhh ~ "relation with the head",
#        if_not_measured_why ~ "Why missing"
#
#     ),
#     statistic = list(
#       all_categorical() ~ "{n} ({p}%)",
#       all_continuous() ~ "{mean} ({sd})"
#     ),
#     missing_text = "(Missing)",
#     digits = everything() ~ c(2,2),
#     missing = "always"
#   ) %>%
#       add_p(test=list(all_continuous() ~ "t.test", all_categorical() ~ "fisher.test.simulate.p.values")) %>%
#       # Modify the table header to provide a descriptive label
#       modify_header(label ~ "Characteristics of children"),
#     # Add difference statistics to the table
#     #add_difference(),
#     .header = "**{strata}**, N = {n}") #%>%
#   #as_gt() %>%
#   #gt::gtsave('desc_table_summary.tex', path = here::here())

```